---
title: "Converting distances measures with distConvert"
author: "Fateema Bazzi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Converting distances measures with distConvert}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
  library(BiocStyle)
```
```{r, echo = FALSE}
  library(knitr)
```
```{r, echo=FALSE}
  library(distConvert)
```
 
# Introduction
Units for measuring distance differ significantly between the European and the US metric systems. The `r Rpackage("distConvert")` package provides functions to convert kilometres to miles and *vice versa*.
# Conversions
## Converting kilometres to miles
Converting **kilometres to miles** is easy as shown in this example:
```{r}
  km_to_miles(1)
```
## Converting miles to kilometres
Converting **miles to kilometres** is just as easy:
```{r}
  miles_to_km(1)
```
A second function provides the same results, but relies on the CRAN package `r CRANpkg("measurements")`:
```{r}
  miles_to_km2(1)
```
